
\noindent
ETH Zurich Admissions Office\\
Raemistrasse 101\\
HG F21\\
8092 Zurich\\
Schweiz\\
\vspace*{20pt}

\noindent
Dear Admissions Office,
\vspace*{10pt}


I am applying for a position in the Mathematics MSc program at ETH Zurich. I am a dedicated student wishing to extend upon my knowledge in the fields of Statistics and Computer Science, with the aspiration to make novel and collaborative contributions to the research community. 
\vspace*{10pt}

I hope to study at ETH Zurich for its impressive history and reputation as an academically rigorous institution, particularly in the scientific fields. I believe I would thrive in an environment surrounded by the caliber of students and faculty at ETH Zurich. Switzerland as a destination is attractive to me for postgraduate studies due to its diversity and inclusiveness. The one year component of in depth studies in the masters programs appeals to me as I wish to develop further specialised knowledge in the field of Mathematics and Statistics. I would also embrace the thesis component to further my independent research skills and prepare for future studies
\vspace*{10pt}

I am studying Statistics and Computer Science for my interest in the power of efficient and intuitive design. I have achieved high standards in my academics, achieving a GPA of 6.88 out of 7 to date, and a perfect 7 for the mathematics component. I have taken time and opportunities to determine my ambitions and motivations, working in industry, volunteer, and research positions. I have also undertaken fulfilling academic exchanges to Japan and France.
\vspace*{10pt}

I have worked as a Data Analyst for a Credit Risk statistical modelling team, where I developed a strong appreciation for the applications of statistics. In my current position as a Research Assistant at Oracle Labs, I am building a graph based knowledge network of open source software vulnerabilities. The most challenging research component of this project is analysing natural language sources through techniques such as Named Entity Recognition. The practical side of my Computer Science degree also complements my theoretical skills, improving the quality, efficiency, and applicability of my research.
\vspace*{10pt}

I have a specific interest in advanced learning models, which leverages my Mathematics and Computer Science background. I aspire to investigate the problem of generalisation in learning models, particularly Natural Language Processing. I want to explore how abstract data structures may be useful for these problems, such as Graph Neural Networks. I also have an interest in Bayesian statistical methods for intractable likelihoods. I am applying for the Mathematics rather than the Computer Science program, as I wish to focus on the fundamental theory and concepts. I believe creative mathematics is the most promising approach to make significant advancements in these modelling techniques.
\vspace*{10pt}

I am a motivated and curious individual who would capitalise on every opportunity ETH Zurich has to offer. I believe my background, abilities, and character makes me ideally suited for your Masters of Science program. Thank you for considering my application.

\vfill
\noindent
Kind regards,
\vspace*{10pt}

\noindent
David Maine