\section*{Education and Experience}
% \noindent\rule{\textwidth}{0.5pt}
\subsection*{Bachelor of Information Technology / Mathematics (2016 - 2020)}

I am currently completing a dual bachelor degree at QUT (Queensland University of Technology) majoring in Statistics and Computer Science.\\
\\
To date I have received a High Distinction with a GPA (Grade Point Average) of 6.880. GPA is on a scale of 1 to 7, where 4 is the minimum passing grade. Exceptional results in mathematics with a GPA of 7 in the mathematics degree component.

\subsubsection*{Involment}

\begin{itemize}
  \setlength\itemsep{0.1em}
  \item QUT Stimulate: As a peer advisor I helped peers with previous subjects studied. This was a rewarding experience that helps greatly with revising previous courses.
  \item QUT Mathematics Society member.
  \item Code Network Society member.
\end{itemize}

\noindent\rule{\textwidth}{0.5pt}

\subsection*{Research Assistant - Oracle Labs (November 2019 - Present)}

I have recently started as a Research Assistant at Oracle Labs Australia. The project I am involved in aims to build an automated system that reports security vulnerabilities in open source software.\\
\\
My research project intends to identify the presence of security patches in application bytecode. Constructing Call Graphs and Control Flow Graphs from bytecode, I am investigating statistical methods to identify key sub graphs (security patches) within application code. This is particularly useful to allow variations in graph pattern matching and has the potential to extend to many other use cases. I also leverage my skills in Big Data Analytics using technologies such as Spark and Kafka to collect and process comprehensive datasets tailored for my research objectives.

\noindent\rule{\textwidth}{0.5pt}

\subsection*{Quantitative Analyst - Bank of Queensland (May 2018 - September 2019)}
I worked as a quantitative analyst at Bank of Queensland in a team responsible for monitoring and modelling credit risk to determine capital and provision requirements for the bank. In this role I developed my technical skills, focusing on data analytics, processing and generalised linear models.\\
\\
This role was my first exposure to real world modelling challenges, showing me the process from beginning to end. I had to learn to apply my skills in a team environment, owning responsibilities and determining the best solutions considering the needs and advice of those around me. 

\noindent\rule{\textwidth}{0.5pt}

\subsection*{Short Term Exchange Program - France (January 2019)}

I attended a short-term exchange to France through the WASAA program. This program consisted of introductory signal processing and AI courses.  

\noindent\rule{\textwidth}{0.5pt}

\subsection*{Teaching Instructor - Code Camp (September 2016 - June 2018)}
I worked as an instructor for Code Camp. Students created small games learning the basics of programming. This was a rewarding experience in which I gained valuable communication and teaching skills. 

\noindent\rule{\textwidth}{0.5pt}

\subsection*{Private Tutoring (January 2017 - June 2018)}
I privately tutored high school students in mathematics. This helped train my ability to communicate ideas and concepts.

\noindent\rule{\textwidth}{0.5pt}

\subsection*{Semester Exchange Program - Japan (September 2017 - Febuary 2018)}
I have completed a semester exchange at Ritsumeikan University in Kyoto, Japan. I built international relationships and have an introductory knowledge of the Japanese language.\\
\\
I received an A average across Japanese Language 1, Japanese economy, society and culture.

\subsubsection*{Involvement}
\begin{itemize}
  \setlength\itemsep{0.1em}
  \item Language Partner: I was involved in a language buddy program with a Japanese student to build both our language skills.
  \item International Activities: Through the international student group I participated in sporting, social and cultural activities.
\end{itemize}

\noindent\rule{\textwidth}{0.5pt}

\subsection*{Teaching Instructor - Junior Engineers (January 2016 - January 2017)}

I worked as an after school teaching instructor for Junior Engineers, teaching classes of primary school students basic concpts of programming through small exercises and games.

\noindent\rule{\textwidth}{0.5pt}

\subsection*{Secondary Education (2012 - 2015)}

I attended Sheldon College located in Queensland, Australia for my secondary education where I received my QCE (Queenslnd Certificate of Education).\\
\\
I received: a VHA (Very High Achievement) in Mathematics, Advanced Mathematics, Physics, Information Technology, Graphics and English; OP (Overall Position) of 1, highest ranking indicating the 97th percentile for the state cohort.

\subsubsection*{Involvement}

\begin{itemize}
  \setlength\itemsep{0.1em}
  \item Student Representative Council.
  \item Arts Program.
  \item Rock Band Guitarist.
\end{itemize}

