\noindent
ETH Zurich Admissions Office\\
Raemistrasse 101\\
HG F21\\
8092 Zurich\\
Schweiz\\
\vspace*{20pt}

\noindent
Dear Admissions Office,
\vspace*{10pt}

I am applying for the ESOP and ETH-D scholarships offered by ETH Zurich. As an international student I am extremely excited at the prospect to study in Zurich, though expenses can be a serious restriction. I believe the standards and opportunities ETH Zurich has to offer is well worth the challenges of studying overseas, and I would hope to continue my studies into the Ph.D program.
\vspace*{10pt}

I am a dedicated student studying Statistics and Computer Science. I have achieved high academic results with a GPA of 6.88 out of 7 to date, and a perfect 7 for the mathematics component. I have also held positions in research and industry, proving my ability to self guide and manage my own projects. I embrace experiencing new cultures and have pushed my comfort zone during exchanges to Japan and France.
\vspace*{10pt}

I have always enjoyed Mathematics, and appreciate how changes in perspective can change the nature and reduce the difficulty of a problem. I also believe my background in Computer Science is closely related, and provides valuable complementary knowledge in data structures, algorithms and complexity.
\vspace*{10pt}

I have recent and relevant experience in research as a Research Assistant at Oracle Labs. I am part of a project to build a graph based knowledge network of open source software vulnerabilities. This position has cemented my interest for a future in research, and I hope to continue to explore the concepts I am working with now in postgraduate study.
\vspace*{10pt}

My current research project at Oracle Labs aims to detect the presence of security patches in Java applications. My approach is to identify sub graphs representing software patches within application call and control flow graphs. Within the project I am exploring techniques such as Graph Neural Network models and spectral graph theory. 
\vspace*{10pt}

In the future I am interested in investigating open problems in the field of Graph Neural Networks. One limitation is the convolutional approach, where the stacking of multiple layers results in over smoothing of the graph dataset, preventing a deep structure. Another challenge is the extension of Graph Neural Network models to dynamic graphs, where the model can adapt to changing nodes and relationships. I have also enjoyed studying Bayesian statistical theory and computational methods, and am interested to understand if the combination of likelihood free inference with Graph Neural Networks is beneficial. 
\vspace*{10pt}



I am a passionate and hardworking student that would benefit greatly from the opportunities your scholarship program has to offer. Thank you for considering my application.

\vfill
\noindent
Kind regards,
\vspace*{10pt}

\noindent
David Maine

